---
title: "0022_Kunanon"
output: html_document
---

Data Analysis Report <br>
Creator : Kunanon Srisuntiroj<br>
Student ID : 59070022<br>
Tuesday Morning Section

In United States of America, there is a lot of varieties of cuisine, which each Americans from each location might not have the same food preferences. The problem is that, we cannot find out where should we open a Thai resteraunt at which area.

Thai cuisines is not an American food nor European. As we are talking, we need to make sure that putting a resteraunt there will generate a profit. But we need more information about the customers also.

To find out, we use data from FiveThirtyThree that have surveys thousands of customers all around America.

Question from the data : <br>
1. Where should a Thai resteraunt open at<br>
2. What's the target group for that Thai resteraunt

# 1 Installing mandatory packages
Package that is not have been installed on the computer will be downloaded.<br>
Package that have been installed will be skipped instead.
```{r Markdown Package Checker}
# It will only install a package THAT IS NOT IN USER COMPUTER.

if (!require("fivethirtyeight"))    install.packages("fivethirtyeight");
if (!require("tidyverse"))          install.packages("tidyverse");
if (!require("gapminder"))          install.packages("gapminder");
if (!require("knitr"))              install.packages("knitr");
```

# 2 Introduction to the dataset
Showing the dataset `food_world_cup` in table
```{r Package Help}
# Show the data tibble of the dataset `food_world_cup`
food_world_cup
```
<br>Which is mostly a customer information and their ratings on the scale of 1 (as not favorable) to 5 (most favorable).

# 3 Search for solution
Starts with getting the data from the dataset and find which area in US loves Thai food the most
```{r Thai Score by location}
# Filtering the data from food_world_cup with no null data set from location or thailand
b2 <- ggplot(data = subset(subset(food_world_cup, thailand != "N/A"),
                           location != "NA"),
             aes(x = location, fill = thailand)) +

    # Create a stack bar graph
    geom_bar(position = "fill") +

    # Lable a stack bar graph
    labs(x = "Location",
         y = "Percentile",
         title = "Thai cuisine score by location",
         subtitle = "Based on a scale of 1 to 5 points given to Thai food. 
People who does not vote at Thailand is excluded.") +

    # Align a lable to 45 degrees + adjust a lable location
    theme(axis.text.x = element_text(angle = 45,
                                     hjust = 1))

b2
```
<br>The bar graph visualizes that people in New England really enjoyed Thai food.<br>
So we will dig down with the data on "Which type of people really loved Thai food".

This graph will shows which age range from New England loves Thai Food. 
```{r Thai score by age, with data from top location}
# Filtering data from food_world_cup with no null dataset and location is 'New England'
b1 <- ggplot(data=subset(subset(food_world_cup, thailand!="N/A"),
                         location == "New England"),
            # Using the data age as x-axis and thailand as y-axis          
             aes(x = age, fill = thailand)) +

# Create Stacked Bar Graph
        geom_bar(position = "fill") +

# Label for the Bar Graph
        labs(x = "Age Range",
             y = "Percentage",
             title = "Thai Cusine score by age",
             subtitle = "Based on a scale of 1 to 5 points given to Thai food. 
People who does not vote at Thailand is excluded.")

b1
```
<br>This can conclude that people age between 18-29 enjoyed Thai food the most.


So another question is that "which gender from 18-29 and lives in New England loves Thai cuisine the most?".
```{r Thai score by gender, with data from gender location}
# Filtering data from food_world_cup with no null dataset and location is 'New England'
b3 <- ggplot(data = subset(subset(subset(food_world_cup, thailand != "N/A"),
                         location == "New England"),
                         age == "18-29"),
             
             # Using gender as x-axis and thailand as y-axis
             aes(x = gender, fill = thailand)) +
    
    # Create a stack bar graph
    geom_bar(position = "fill") +

    # Label a stack bar graph
    labs(x = "Gender",
         y = "Percentage",
         title = "Thai Cuisine score by gender",
         subtitle = "Based on a scale of 1 to 5 points given to Thai food. 
People who does not vote at Thailand is excluded.")

b3
```

# Conclusions
When about to open a Thai resteraunt, there is a good chance that open at New England is the best deal.<br>
Main customer ages about 18-29 Female. <br>

With this data, we can safely sure that New England does have a lot of strong demand in Thai food. This confirms by the Google review made by user in New England area.

# References <br>
Data Reference <br>
https://cran.r-project.org/web/packages/fivethirtyeight/index.html<br>
https://fivethirtyeight.com/features/what-is-americans-favorite-global-cuisine/<br>
https://fivethirtyeight.com/features/the-fivethirtyeight-international-food-associations-2014-world-cup/<br>
https://github.com/fivethirtyeight/data/tree/master/food-world-cup<br>

Code Reference<br>
Creating stack bar graph <br>http://rstudio-pubs-static.s3.amazonaws.com/3256_bb10db1440724dac8fa40da5e658ada5.html<br>
Left data text alignment <br>https://www.statmethods.net/advgraphs/axes.html
