---
title: "0022_Kunanon"
output: html_document
---

Data Analysis Report <br>
Creator : Kunanon Srisuntiroj<br>
Student ID : 59070022<br>
Tuesday Morning Section

In United Kingdom, there is a lot of varieties of cousines and we cannot find out where should we locate a resteraunt.<br>
Thai cousine is one of the exotic food cousines in the world, but we still can't figured out where should we place down a resteraunt.<br>
To find out, we use data from surveys to extract on what they liked and planned ahead for maximum profit and constant eaters.

Question from the data :
1. Where should a Thai resteraunt open at
2. What's the target group for that Thai resteraunt

# 1 Checking for mandatory packages
A computer that does not install a package yet, it will install a package.<br>
Package that have been installed will be skipped.
```{r Markdown Package Checker}
# It will only install a package THAT IS NOT IN USER COMPUTER.

if (!require("fivethirtyeight"))    install.packages("fivethirtyeight");
if (!require("tidyverse"))          install.packages("tidyverse");
if (!require("gapminder"))          install.packages("gapminder");
if (!require("knitr"))              install.packages("knitr");
if (!require("lintr"))              install.packages("lintr");
```

# 2 Introduction to the dataset
```{r Package Help}
# Show the data tibble of the dataset `food_world_cup`
food_world_cup
```

# 3 Search for solution
Starts with getting the data from the dataset and find which town loves Thai food the most
```{r Thai Score by location}
      # Filtering the data from food_world_cup with no null data set from location or thailand
b2 <- ggplot(data = subset(subset(food_world_cup, thailand != "N/A"),
                         location == "New England"),
             # Using the data age as x-axis and thailand as y-axis
             aes(x = age, fill = thailand)) +

    # Create Stacked Bar Graph
    geom_bar(position = "fill") +

    # Lable for the Bar Graph
    labs(x = "Age Range",
         y = "Percentage",
         title = "Thai Cusine score by age")

b2
```

```{r Thai score by age, with data from top location}
    # Filtering data from food_world_cup with no null dataset and location is 'New England'
b2 <- ggplot(data=subset(subset(food_world_cup, thailand!="N/A"),
                         location == "New England"),
            # Using the data age as x-axis and thailand as y-axis          
             aes(x = age, fill = thailand)) +

# Create Stacked Bar Graph
        geom_bar(position = "fill") +

# Lable for the Bar Graph
        labs(x = "Age Range",
             y = "Percentage",
             title = "Thai Cusine score by age")

b2
```

```{r Thai score by gender, with data from gender location}
    # Filtering data from food_world_cup with no null dataset and location is 'New England'
b2 <- ggplot(data = subset(subset(food_world_cup, thailand != "N/A"),
                         location == "New England"),
             # Using the data gender as x-axis and thailand as y-axis
             aes(x = gender, fill = thailand)) +

    geom_bar(position = "fill") +

    labs(x = "Gender",
         y = "Percentage",
         title = "Thai Cuisine score by gender") +

    theme(axis.text.x = element_text(angle = 45, hjust = 1))

b2
```

# References <br>
Data Reference <br>
https://cran.r-project.org/web/packages/fivethirtyeight/index.html<br>

Code Reference<br>
Creating stack bar graph <br>http://rstudio-pubs-static.s3.amazonaws.com/3256_bb10db1440724dac8fa40da5e658ada5.html<br>
Left data text alignment <br>https://www.statmethods.net/advgraphs/axes.html
